\documentclass{article}

\usepackage{parskip}
\usepackage[table]{xcolor}
\usepackage{longtable}

\definecolor{vertdigital}{HTML}{48995c}
\definecolor{jaunedigital}{HTML}{ffb13b}
\definecolor{vertprint}{HTML}{007d0c}
\definecolor{jauneprint}{HTML}{ffa51f}
\definecolor{marron}{HTML}{885138}

\title{pachatopia.org whitepapaer}
\author{Cătălin Tișcă}

\begin{document}

\maketitle

\section{introduction}
\textbf{Pachatopia} is an association that creates nature reserves and promotes 
sustainable agriculture and eco-responsible living, inspired by Indigenous respect for the Earth.

Pachatopia is building a \textit{blockchain-based map} to track its land use, allowing donors to own
land parcels and receive on-chain rights to their produce, community membership, and educational
access—advancing ReFi accountability while laying the groundwork for a genetic bank preserving the 
region's unique plant biodiversity.

\section{technical implementation}

\subsection{design}

The visual identity of Pachatopia is rooted in its tagline \textit{``El Mundo Es Uno Solo''}
(The World Is One) and its Latin motto \textit{``Sub Patriocinio Fuit --- De Amore Et Gracia''}.
Founded in 2022, the brand communicates earth stewardship, warmth, and agricultural heritage
through a deliberate palette, typographic system, and logo framework.

\subsubsection{color palette}

Two palette variants exist depending on medium. A shared brown bridges both contexts.

\begin{longtable}{l l l l}
\textbf{Context} & \textbf{Color} & \textbf{Hex} & \textbf{Swatch} \\
\hline
Digital / web / social & Vert n\textsuperscript{o}1 (primary green) & \texttt{\#48995c} & \colorbox{vertdigital}{\hspace{1.5cm}\strut} \\
Digital / web / social & Jaune orang\'e n\textsuperscript{o}1 (primary orange-yellow) & \texttt{\#ffb13b} & \colorbox{jaunedigital}{\hspace{1.5cm}\strut} \\
\hline
Print / labels / invoices & Vert n\textsuperscript{o}2 (darker green) & \texttt{\#007d0c} & \colorbox{vertprint}{\hspace{1.5cm}\strut} \\
Print / labels / invoices & Jaune orang\'e n\textsuperscript{o}2 (deeper orange-yellow) & \texttt{\#ffa51f} & \colorbox{jauneprint}{\hspace{1.5cm}\strut} \\
\hline
Shared (all contexts) & Marron (brown) & \texttt{\#885138} & \colorbox{marron}{\hspace{1.5cm}\strut} \\
\end{longtable}

\subsubsection{typography}

\begin{itemize}
    \item \textbf{Lora} --- logo wordmark
    \item \textbf{Fraunces} --- titles and headings
    \item \textbf{Hatton} --- body text
\end{itemize}

\subsubsection{logo}

The logo is an oval badge containing a coffee bean (orange-yellow) above two leaves, with sun
rays at the top and rolling hills/fields at the bottom. \textit{``El Mundo Es Uno Solo''} arcs
above the emblem; \textit{``ESTD''} appears on the left and \textit{``2022''} on the right.
\textit{``. PACHATOPIA .''} is set below in caps.

Three logo variants are defined for different use cases:

\begin{itemize}
    \item \textbf{Digital / media} --- white linework on a green background (\texttt{\#48995c})
    \item \textbf{Invoices / admin docs} --- dark green linework on a white or light background
    \item \textbf{Coffee labels} --- brown linework (\texttt{\#885138}) on kraft or cream paper
\end{itemize}

\subsubsection{product branding (coffee)}

Coffee packaging carries \textit{``. PACHATOPIA . COFFEE --- Colombia''} beneath the logo.
Key product details:

\begin{itemize}
    \item \textbf{Origin:} Antioquia, Colombia, 1\,400\,m altitude
    \item \textbf{Variety:} Arabica
    \item \textbf{Roast levels:} three levels, each indicated with flame icons
\end{itemize}

\subsection{web2 details}
Pretty much the frontend and the backend concerns of the app. A backend is still required, as it is too
early to go for a decentralized storage infrastructure like \textit{IPFS}

\subsubsection{tech stack}
\begin{itemize}
    \item \textbf{Vite + React} - fully open source frontend library, universal choice
    \item \textbf{TailwindCSS + shadcn} - allows enough customization \& flexibility for getting the UI done right
    \item \textbf{ConvexDB \& @convex/auth} - prolly the best option nowadays
    \item \textbf{react-leaflet} - React integration
    \item \textbf{leaflet-draw} - admin polygon drawing/editing
    \item \textbf{turf.js} - geospatial calculations (area in m², parcel splitting, overlap detection)
\end{itemize}

\subsection{blockchain infra}
KISS \textit{(keep it simple stupid)}, everything on the ethereum chain can be done quite easily.
\begin{itemize}
    \item \textbf{ERC-721} - each m² is unique, this is the perfect standard to identify each one of them
    \item \textbf{Guild.xyz} - the gatekeeper, provides an \textit{identity portal}
    \item \textbf{Snapshot} - gasless voting, good for establishing the \textit{DAO}
\end{itemize}

\end{document}